Guidelines and Policy for the Dark Energy Survey Strong Lensing Science Team using \SW

### 2015-03-28 doc/sw-publication-policy-des.tex
SW-DES policy doc

\subsection{Previewing images}
We are aware that there is some interest in the DES SST for using \SW web interface to preview images for the SST themselves. As this is not the function of the \SW interface or the Zooniverse, this would only be possible under certain conditions:
\begin{enumerate}[label=(\alph*)]
\item the images inspected are destined to be seen by the crowd either in parallel with the SST;
\item the framework of the image presentation (i.e the \SW interface) is the same as the interface presented to the user (image clicks only and no comments or ranking possible);
\item all SST inspectors would have to register with the Zooniverse to classify;
\item While we would not distribute the URL to community, we cannot password protect the site. Note the data can still be stripped of WCS information (please see Section \ref{sec:data} for more information.).
\end{enumerate}

>>>>

\subsection{Previewing images}
We are aware that there is some interest in the DES SST for using \SW web interface to preview images for the SST themselves. As this is not the function of the \SW interface or the Zooniverse, this would only be possible under certain conditions:
\begin{enumerate}[label=(\alph*)]
\item the images\footnote{can still be stripped of WCS information (please see Section \ref{sec:data}} inspected are destined to be seen by the crowd  \textbf{in parallel} with the SST, therefore the URL for the inspection will be publicly available.;
\item the framework of the image presentation (i.e the \SW interface) is the same as the interface presented to the volunteers (image clicks only and no comments or ranking possible);
\item all SST inspectors would have to register with the Zooniverse to classify.
\end{enumerate}
